\LARGE BAND\\ \Large Unleashing Tokenized Economy

### 2018-02-20 paper.tex
Bump version: 0.1.0
Add Introduction - Tokenized Economy

\title{\LARGE BAND\\
    \Large Unleashing Tokenized Economy}
\author{
        Soravis Srinawakoon\\
        \small\href{mailto:soravis@bandprotocol.com}
            {\nolinkurl{soravis@bandprotocol.com}}
    \and
        Sorawit Suriyakarn\\
        \small\href{mailto:swit@bandprotocol.com}
            {\nolinkurl{swit@bandprotocol.com}}
    }
\date{\today\\\small Draft Version 0.0.0}
\begin{document}

@@

>>>>

\title{\LARGE BAND\\
    \Large Unleashing Tokenized Economy}
\author{
        Soravis Srinawakoon\\
        \small\href{mailto:soravis@bandprotocol.com}
            {\nolinkurl{soravis@bandprotocol.com}}
    \and
        Sorawit Suriyakarn\\
        \small\href{mailto:swit@bandprotocol.com}
            {\nolinkurl{swit@bandprotocol.com}}
    }
\date{\today\\\small Draft Version 0.1.0}
\begin{document}

@@

A typical market-based economy involves the exchange of goods and services through barter or a medium of exchange. Traditionally, buyers exchange physical coins and banknote with physical products or services offered by sellers. As technology progresses, Internet has enabled digital economy whereby goods and services are being exchanged with digital money. E-commerce experiences exponential growth as people can conveniently conduct transaction with people across the world. Centralized companies start to dominate marketplace platform and payment gateway which are key enablers of the digital economy.

Blockchain and crypto assets are giving rise to yet another revolution in the economy. Bitcoin~\cite{nakamoto}, the first cryptocurrency, becomes the first decentralized currency which enables trustless, censorship-resistant payment. Cryptocurrency such as Bitcoin allows anyone to send transaction to anyone around the world at a fraction of a cost and a fraction of time required for traditional financial institutions to conduct similar transaction. As payment and currency are being tokenized, traditional asset is slower to experience similar tokenization process. Regulation and usability are two key factors that hinder the explosive growth of asset tokenization. Asset tokenization has clear benefits:
\begin{itemize}
\item Global accessibility
\item Liquidity premium
\item Low transaction fee
\item Transparency
\item Security
\end{itemize}

Similar to how physical trade transitions to digital trade by the advancement of the Internet, the next era of commerce is the transition from centralized digital trade to decentralized token trade. Tokenized economy will become prevalent as both real-world assets and payment are being tokenized. Band Protocol enables asset tokenization and creates a standard platform for tokenized economy.
\newpage
